Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-02-09 ms.tex
pt profile fig

\section{Results}
\label{sec:results}
The fitted light curves are shown in Figure\,\ref{fig:phasecurves}. This figure shows results from the spherical harmonics model for the thermal phase variation and has instrument systematics removed.  Broadly speaking, the phase curves show large dayside planet-to-star flux values, ranging from $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 white light curve, and \Spitzer\ $3.6$, and $4.5\mu$m bandpasses, respectively.  The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5. In this section, we quantitatively characterize the phase curve shape, split the data into phase resolved spectra, evaluate different temperature maps, and compare with previous observations of the dayside thermal emission spectrum.

@@

The best fit model is generally the spherical harmonics map. It has a lower BIC value than all the other models for the broadband WFC3 and \Spitzer\,$3.6\,\mu$m phase curves. For the $4.5\,\mu$m phase curve, the two temperature map provides the best fit, but it only lowers the BIC value by 2 relative to the spherical harmonics map, which is not a statistically significant improvement \citep{kass95}. The spherical harmonics model yields a mean dayside temperature near 2700 K, whereas the nightside is closer to 1800 K.  The other models produce more extreme day-night temperature gradients.  These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.  The intermediate temperature gradient in the spherical harmonics model fits the data the best. However, this model may not be physically realistic: on the nightside, it produces much higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).

@@

>>>>

\section{Results}
\label{sec:results}
The fitted light curves are shown in Figure\,\ref{fig:phasecurves}. This figure shows results from the spherical harmonics model for the thermal phase variation and has instrument systematics removed.  Broadly speaking, the phase curves show large dayside planet-to-star flux values, ranging from $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 white light curve, and \Spitzer\ $3.6$, and $4.5\mu$m bandpasses, respectively.  The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5. In this section, we quantitatively characterize the phase curve shape, split the data into phase resolved spectra, evaluate different temperature maps, compare with previous observations of the dayside thermal emission spectrum, and report the transmission spectrum.

@@

The spherical harmonics map generally fits the data the best. It has a lower BIC value than all the other models for the broadband WFC3 and \Spitzer\,$3.6\,\mu$m phase curves. For the $4.5\,\mu$m phase curve, the two temperature map provides the best fit, but it only lowers the BIC value by 2 relative to the spherical harmonics map, which is not a statistically significant improvement \citep{kass95}. The worst fit model is gene FIXME

The spherical harmonics model yields a mean dayside temperature near 2700 K, whereas the nightside is closer to 1800 K.  The other models produce more extreme day-night temperature gradients.  These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.  The intermediate temperature gradient in the spherical harmonics model fits the data the best. However, this model may not be physically realistic: on the nightside, it produces much higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).

@@

We compared the TP profiles from the GCM to cloud condensation curves and the best fit radiative-convective equilibrium models from the 1D retrieval (Figure\,\ref{fig:TP}).

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b-NoClouds-Drag3-nit-LR.pdf}
\caption{TP profiles from the GCM (thin colored lines) and 1D retrievals (thick lines), compared to condensation curves of potential cloud species. The blue, green, and red lines correspond to TP profiles randomly drawn from the FIXME GCM at orbital phases FIXME. The thick red and blue lines are the best fit 1D TP profiles for the dayside ($\phi = 0.5$) and nightside ($\phi = 0.1$), respectively.}
\label{fig:TP}
\end{figure}
